Pool Model

### 2025-08-28 pool_model.tex
more cleanup; more formatting for twocolumn layout

\setlength{\tabcolsep}{1.3pt}
\usepackage{acronym}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[
    backend=biber,
    sorting=none,
    style=numeric-comp,
    hyperref=true,
    maxnames=2,
    url=false,
    isbn=false,
    eprint=false,
    date=year,
    doi=false,
    giveninits=true
]{biblatex}
\usepackage{array}
\usepackage{bm}
\usepackage{booktabs}
\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off, font=small]{caption}
\usepackage{color}
\usepackage{ctable} % for \specialrule command
\usepackage{diagbox}
\usepackage{float}
\usepackage[T1]{fontenc}
\usepackage[a4paper,inner=2.5cm,outer=3cm]{geometry}
\usepackage{graphicx}% Include figure files
\usepackage{here}
\usepackage{hyperref}
\usepackage{lipsum}
\usepackage{listings}
\usepackage{listings-rust}
\usepackage{mathtools}
\usepackage{mathrsfs}
\usepackage{multirow}
\usepackage{newfloat}
\usepackage{siunitx}
\usepackage{subcaption}
\usepackage{tabularx}
\usepackage[dvipsnames]{xcolor}
\usepackage{xpatch}

@@

    \includegraphics[width=\columnwidth]{Figures/TPM_fig.pdf}

@@

    \includegraphics[width=\columnwidth]{Figures/pool_model_3pools_resource.pdf}

@@

\label{eq:reactions_backlag}

@@

    \dot{\gamma} &=& \Gamma \left |\dot{T}\right |-\delta \gamma.
\label{eq:rate_backlag}

@@

    \gamma(t) &=& \Gamma \int_0^t \left |\dot{T}(t^{\prime})\right |e^{-\delta (t-t^{\prime})}dt^{\prime}.
\label{eq:rate_backlag2}

@@

    \gamma(t) &=& \Gamma\delta\left |\left[T[t]-T[0]e^{-\delta t}-\delta \int_0^t T(t^{\prime})e^{-\delta (t-t^{\prime})}dt^{\prime}\right]\right |.
\label{eq:rate_backlag3}

@@

    \dot{L} =\gamma(t) G - (\mu + \lambda) L\\
    \dot{G} = \lambda L -\gamma(t) G + \alpha G\left(1-\frac{L+G+D}{N_t}\right)\\
    \dot{D} = \mu  L - \beta D

@@

    \includegraphics[width=\columnwidth]{Figures/pool_model_3pools_resource_tempshift.pdf}

@@

\newpage

@@

        \dot{L}_A = - \lambda_A R L_A\\
        \dot{L}_B = - \lambda_B R L_B \\
        \dot{G}_A = \lambda_A R L_A +\alpha_A R G_A\\
        \dot{G}_B = \lambda_B R L_B +\alpha_B R G_B\\
        \dot{R} =-\frac{\alpha_A}{N_t} R G_A-\frac{\alpha_B}{N_t} R G_B

@@

@@

R &=&1-\frac{L_A+G_A+L_B+G_B}{N_t}

@@

\begin{eqnarray*}
    \dot{L}_A &=& - \lambda_A  L_A + \frac{\lambda_A}{N_t}L_A\left<LG\right>\\
    \dot{L}_B &=& - \lambda_B L_B + \frac{\lambda_B}{N_t}L_B \left<LG\right>\\
    \dot{G}_A &=&  \lambda_A  L_A + \alpha_A G_A - \frac{\lambda_A L_A + \alpha_A G_A}{N_t} \left<LG\right>\\
    \dot{G}_B &=&  \lambda_B L_B - \alpha_B G_B \frac{\lambda_B L_B + \alpha_B G_B}{N_t}\left<LG\right>
\end{eqnarray*}

@@

    \includegraphics[width=\columnwidth]{Figures/pool_model_2pools_resource_competition.pdf}

@@

@@

    \includegraphics[width=\columnwidth]{Figures/pool_model_2pools_toxin.pdf}

@@

@@

    \includegraphics[width=\columnwidth]{Figures/pool_model_1pool_inhib.pdf}

@@

    \includegraphics[width=\columnwidth]{Figures/pool_model_2sp_1pool_coop.pdf}

@@

        \includegraphics[width=\columnwidth]{Figures/abm-homogenous/abm_ode_comparison.png}

@@

        \includegraphics[width=\columnwidth]{Figures/abm-homogenous-low-diffusion/abm_ode_comparison.png}

@@

        \includegraphics[width=\columnwidth]{Figures/abm-inhomogenous/abm_ode_comparison.png}%

@@

        \includegraphics[width=\columnwidth]{Figures/abm-random/abm_ode_comparison.png}%

>>>>

\setlength{\tabcolsep}{1.3pt}
\usepackage{acronym}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[
    backend=biber,
    sorting=none,
    style=numeric-comp,
    hyperref=true,
    maxnames=2,
    url=false,
    isbn=false,
    eprint=false,
    date=year,
    doi=false,
    giveninits=true
]{biblatex}
\usepackage{array}
\usepackage{bm}
\usepackage{booktabs}
\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off, font=small]{caption}
\usepackage{color}
\usepackage{ctable} % for \specialrule command
\usepackage{diagbox}
\usepackage{float}
\usepackage[T1]{fontenc}
\usepackage[a4paper,inner=2cm,outer=2cm]{geometry}
\usepackage{graphicx}% Include figure files
\usepackage{here}
\usepackage{hyperref}
\usepackage{lipsum}
\usepackage{listings}
\usepackage{listings-rust}
\usepackage{mathtools}
\usepackage{mathrsfs}
\usepackage{multirow}
\usepackage{newfloat}
\usepackage{siunitx}
\usepackage{subcaption}
\usepackage{tabularx}
\usepackage[dvipsnames]{xcolor}
\usepackage{xpatch}

@@

    \includegraphics[width=0.9\columnwidth]{Figures/TPM_fig.pdf}

@@

    \includegraphics[width=0.9\columnwidth]{Figures/pool_model_3pools_resource.pdf}

@@

@@

    \dot{\gamma} = \Gamma |\dot{T}|-\delta \gamma.

@@

    \gamma(t) = \Gamma \int_0^t |\dot{T}(t^{\prime})|e^{-\delta (t-t^{\prime})}dt^{\prime}.

@@

    \gamma(t) = \Gamma\delta\left |T[t]-T[0]e^{-\delta t}-\delta
        \int\limits_0^t T(t^{\prime})e^{-\delta (t-t^{\prime})}dt^{\prime}\right |.

@@

        \dot{L} &=\gamma(t) G - (\mu + \lambda) L\\
        \dot{G} &= \lambda L -\gamma(t) G + \alpha G\left(1-\frac{L+G+D}{N_t}\right)\\
        \dot{D} &= \mu  L - \beta D

@@

    \includegraphics[width=0.9\columnwidth]{Figures/pool_model_3pools_resource_tempshift.pdf}

@@

@@

        \dot{G}_A &= \lambda_A R L_A +\alpha_A R G_A\\
        \dot{G}_B &= \lambda_B R L_B +\alpha_B R G_B\\
        \dot{R} &=-\frac{\alpha_A}{N_t} R G_A-\frac{\alpha_B}{N_t} R G_B

@@

    R =1-\frac{L_A+G_A+L_B+G_B}{N_t}

@@

@@

    \dot{L}_A &= -\lambda_A  L_A + \frac{\lambda_A}{N_t}L_A\left<LG\right>\\
    \dot{L}_B &= -\lambda_B L_B + \frac{\lambda_B}{N_t}L_B \left<LG\right>\\
    \dot{G}_A &=  \lambda_A  L_A + \alpha_A G_A - \frac{\lambda_A L_A + \alpha_A G_A}{N_t} \left<LG\right>\\
    \dot{G}_B &=  \lambda_B L_B - \alpha_B G_B \frac{\lambda_B L_B + \alpha_B G_B}{N_t}\left<LG\right>

@@

    \includegraphics[width=0.9\columnwidth]{Figures/pool_model_2pools_resource_competition.pdf}

@@

\begin{figure*}[t!]

@@

    \includegraphics[width=2.0\columnwidth]{Figures/pool_model_2pools_toxin.pdf}

@@

\end{figure*}

@@

    \includegraphics[width=0.9\columnwidth]{Figures/pool_model_1pool_inhib.pdf}

@@

    \includegraphics[width=0.9\columnwidth]{Figures/pool_model_2sp_1pool_coop.pdf}

@@

        \includegraphics[width=0.9\columnwidth]{Figures/abm-homogenous/abm_ode_comparison.png}

@@

        \includegraphics[width=0.9\columnwidth]{Figures/abm-homogenous-low-diffusion/abm_ode_comparison.png}

@@

        \includegraphics[width=0.9\columnwidth]{Figures/abm-inhomogenous/abm_ode_comparison.png}%

@@

        \includegraphics[width=0.9\columnwidth]{Figures/abm-random/abm_ode_comparison.png}%
